Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-09-11 writeup/gz_hubble_data.tex
Figures 7 and 8 added

\subsection{Results of Zeta Approach (Mel stuff)}

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

@@

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).

>>>>

\subsection{Results of $\zeta$ approach}

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

@@

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).
